Features for detecting threats of violence in YouTube comments

### 2016-03-30 submission.tex
Made changes discussed in last meeting

% Author information can be set in various styles:
% For several authors from the same institution:
\author{Aksel Wester \and Lilja Øvrelid \and Erik Velldal \\
        University of Oslo \\ ... \\ Address line}
% if the names do not fit well on one line use

@@

@@

    \end{tabular}
  \end{center}
  \caption{F-scores of the bag of words, and bag of words and lemma feature sets, combined with word form bigrams, trigrams or both.}
  \label{tab:ngrams}
  % tidligere Tabell 4
\end{table}

@@

    \end{tabular}
  \end{center}
  \caption{Results of bag of feature variations with different feature types. The results shown are the F-scores of each feature set after tuning, using the MaxEnt classifier.}
  \label{tab:bagOfFeatures}
  % tidligere Tabell 3
\end{table}

>>>>

% Author information can be set in various styles:
% For several authors from the same institution:
\author{Aksel Wester \and Lilja Øvrelid \and Erik Velldal \\
  Department of Informatics \\
  University of Oslo, Norway \\
  ... \\
  \{aksellw, liljao, erikve\}@ifi.uio.no}
% if the names do not fit well on one line use

@@

We use a simple count-based feature reduction on the features in each feature set, where we include in the feature set only the features the appear at least twice in the training data.

@@

    \end{tabular}
  \end{center}
  \caption{F-scores of the bag of words feature set, with different combinations of the other feature sets tested in Table \ref{tab:baseline}.}
  \label{tab:ngrams}
  % tidligere Tabell 4
\end{table}

@@

    \end{tabular}
  \end{center}
  \caption{F-scores of bag of features (BoF) with and without bag of words (BoW). POS\textsubscript{Lex} and Dep\textsubscript{Lex} are lexicalized POS and dep-tags, respectively, where each feature is a tuple consisting of the tag and the word form of the token.}
  \label{tab:bagOfFeatures}
  % tidligere Tabell 3
\end{table}
